---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# impenrich

<!-- badges: start -->

<!-- badges: end -->

The main function of this R package is to supplement Yulab enricher, as well as some other middleware. It is mainly for personal use and recording. If I don't record it, I will forget it all.

## Installation

You can install the development version of impenrich from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ixxmu/implenrich")
```
To cite fanyi in publications use:

G Yu. Using fanyi to assist research communities in retrieving and interpreting information. **_bioRxiv_**, 2023. doi: [10.1101/2023.12.21.572729](https://www.biorxiv.org/content/10.1101/2023.12.21.572729).

## :writing_hand: Authors

## :beginner: Usages

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(impenrich)
## basic example code
```
